Multi-Index and Multi-Level Monte Carlo Evaluation of HJM Models

### 2016-05-07 tests/HJM/manuscript.tex
fig 3 replot

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr1.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr1.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{fig:rateFig1} Weak (left) and strong (right) error
    $\nnorm{\int_0^T f \parent{s,s} ds - \lim_{N_t \rightarrow \infty} F_{N_t,N_f}}{}$. $N_t= 2^9+1$.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$.}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr1.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr1.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{fig:rateFig1} Weak (left) and strong (right) error
    $\nnorm{F_{513,2N_f} - F_{513,N_f}}{}$ along with $N_f^{-\frac{3}{2}}$ and
    	$N_f^{3}$ reference lines in red.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$ together with the $N_f^{-\frac{3}{2}}$ and
    $N_f^{-3}$ reference lines in red.}
\end{figure}
